Distributed Decision Making for Dynamic Formation of Communities of Web Services

### 2015-06-28 papers/webservice-coalition-learning-submitted-r0/elsarticle-template-num.tex
changes

\author{
    \IEEEauthorblockN{\normalsize Ehsan Khosrowshahi Asl\IEEEauthorrefmark{1}, Babak Khosravifar\IEEEauthorrefmark{1}, Jamal Bentahar\IEEEauthorrefmark{1}, Hadi Otrok\IEEEauthorrefmark{2}, Rabeb Mizouni\IEEEauthorrefmark{2}}\\
    \IEEEauthorblockA{\IEEEauthorrefmark{1}Concordia Institute for Information Systems Engineering, Concordia University, Montreal, Canada}
    \\
    \IEEEauthorblockA{\IEEEauthorrefmark{2}Department of Electrical and Computer Engineering, KUSTAR, Abu Dhabi, UAE}
}
\title{Distributed Decision Making for Dynamic Formation of Web Services Communities}

@@

\begin{abstract}
Web services are loosely-coupled business applications willing to cooperate in distributed settings within different groups called communities. Communities aim to provide web services with better visibility, efficiency, market share and total payoff. A number of mechanisms and models have been recently proposed to aggregate web
services and make them cooperate within their communities. However, existing community models mostly focus on short-term utility gain. Moreover, these models generally suffer from high computational complexity, which makes decision making about community formation in real-time extremely hard, time consuming, and even impossible in some complex cases. In this paper, we propose a strategic distributed decision making mechanism called DDM that regulates web service agents' decision making process, which is about deciding with whom to cooperate. This model first generates a trained set of data based on information obtained from large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc. The decision making mechanism implements a decision tree of possible viable strategies and their long-term expected utility gain.
%Utilizing the training model, the decision making mechanism implements a decision tree with an estimation of long-term utility gain for the web services. Communities can used the trained model and instantly choose best-response strategies considering their long-term gain. 
Our model helps 1) communities of web services efficiently find the appropriate web service to invite as new member; and 2) single web services find best communities to join. After being trained, web services get to compute expectations as utilities they would gain if they cooperate with communities of different characteristics. In contrast, communities can take the training into account and analyze the characteristics of different individual web services and make prudent decisions when inviting a web service to join or accepting a join inquiry initiated by a web service. In general, DDM equips web services with efficient methods of foreseeing how their choices of actions would impact their short-term and long-term goals, therefore opting for better decisions. We performed experiments using real data from 142 users on 4,532 web services during 64 different time slots. The experimental results show that our algorithms provide web services and community owners, in real-world-like environments, with applicable and near-optimal decision making mechanisms.
\end{abstract}
\begin{IEEEkeywords}
Web services; Community of services; Distributed decision making;
\end{IEEEkeywords}

@@

\textbf{Challenges and Problem Statement.} In recent work, communities of web services have been proposed in order to facilitate discovery of web services, improve the Quality of Service (QoS), and help individual services find better market share and opportunities \cite{Zeng:2003:QDW:775152.775211, 10.1109/ARES.2008.7, Paik:2005:TSS:2229263.2230038, Medjahed05adynamic}. However,  two important challenges are to be addressed: 1) choice of the best web services during community development from the community perspective; and 2) choice of the best community to join from the web service perspective. The advocated solutions  \cite{10.1109/ARES.2008.7, conf/webist/MaamarLBTS07, journals/soca/XuYLZB11, 10.1109/TSC.2012.12, managing-hela-jalel, DBLP:conf/IEEEscc/KhosravifarABT11, DBLP:conf/IEEEscc/LimTMB12} have attempted to address these challenges. However, those solutions have two main limits: 
\begin{enumerate}
	\item The solutions consider the architecture of centralized management for communities where most of the decisions are made by the centralized coordinator. The problem is that in real world scenarios, decisions made by independent service providers are highly distributed.
	\item The solutions either propose complex algorithms \cite{10.1109/TSC.2012.12, DBLP:conf/IEEEscc/LimTMB12, 10.1109/TSC.2014.2312940} to find the optimal strategy to follow, or oversimplify the problem by eliminating important parameters and using approximation techniques to make the algorithms tractable \cite{10.1109/TSC.2012.12}.
\end{enumerate}
These approximation methods sometimes negatively influence the outcome because simplifying the constraints may cause important aspects of the problem to be ignored. For instance, instead of calculating the gain distribution using the adequate, but complex shapely-value method, the authors is \cite{10.1109/TSC.2012.12} propose a simple egalitarian way of distributing gain, which completely ignores the gain generated from collaborative work of sub-communities. Other categories of related work, for instance \cite{10.1109/TSC.2012.12, DBLP:conf/IEEEscc/KhosravifarABT11, DBLP:journals/ijebr/MaamarSTBB09}, restrict the decision process within the community coordinator, so other members of the community are not effectively involved. 
%And some other work which do not focus on rationality on web services or communities involved [refrences]. 
In \cite{journal-community-formation}, we proposed a cooperative game-theory-based model for aggregating web services in communities. A centralized decision maker in communities, based on a complete knowledge of available web service quality metrics and performance, has been used to form optimal and stable communities that maximize individual and group income. However, centrality and complete information are strong assumptions, which are not very compatible with real business scenarios.

@@

\subsection{The Join Challenge}\label{s:tjc} 
It has been showed in \cite{10.1109/ARES.2008.7,10.1109/TSC.2012.12,10.1109/TSC.2014.2312940} that web services can increase their overall utility by collaborating with other web services within communities. This collaboration provides them with better ways of sharing resources and having higher reputation, greater market share and wider visibility. Web services and communities come with different quality metrics, and the long-term outcome depends on these metrics.

@@

\begin{figure}%[!t]
\centerline{\includegraphics[width=5.25in]{figures/steps.eps}}
\caption{A summary of DDM decision profile generation steps}
\label{fig_steps}
\end{figure}

@@

In \cite{10.1109/TSC.2012.12}, a cooperative scheme among
autonomous web services based on coalitional game theory has been
introduced. The authors have proposed an interesting algorithm to
reach individually stable coalition partition for web services in
order to maximize their efficiency. The communities choose new web
services on the promise that it would benefit the community
without decreasing any other web service's income. In the proposed
model, the worth of community is evaluated with high emphasis on
the availability metric and considering price and cost values
only. The community structure is based on a coordination chain,
where a web service is considered as a \emph{primary} web service
and the community task-distribution method initially invokes the
primary web service and only if the primary web service is
unavailable, the method invokes the next backup web services as
they are ordered in the coordination chain. We believe that this
coordination chain limits the cooperation power as it introduces a
sort of hierarchy. However, in pure and open cooperative models,
such as the one we propose in this paper, active cooperation
activities engaging simultaneously many agents so that they can
perform the tasks more efficiently are being used. Moreover, if
the availability is high, which is the case nowadays with the
recent advancements in cloud and hardware infrastructures, the
backup web services will end-up having a very low chance of
getting jobs, especially the ones further in the chain. This will
results in a considerable waste of web services capabilities.

All the proposed frameworks share a common aspect, which is providing the solution based on assumption of having complete information of all services and performing evaluations based on a large number of input each time they want to adopt a strategic decision making process. 
So basically These solutions generally suffer from high complexity, which makes decision making impossible in an on-demand fashion, or they simplify important aspects to make it practical in the real world, thereby hurting the decision making performance. We address this issue by introducing DDM a framework that operates based on a trained model that regulates web service agents' decision making process in terms of cooperating with one another. After being trained, web services get to compute expectations as utilities they would gain while cooperating with communities of different characteristics. Therefore web services and communities can make prudent decisions when inviting a web service to join or accepting a join inquiry initiated from a web service. In general, DDM equips web services with efficient methods for foreseeing how their choices will impact their long-term and short-term goals; therefore, opting for best decision available. \\

@@

Here we introduce the related research work regarding the engineering and formation of communities of web services. In \cite{DBLP:journals/internet/BenatallahSD03}, Benatallah et al. defined communities of web services as \emph{Service Containers} that aggregate substitutable web services providing a common functionality (same
set of operations). They abstracted \emph{Service Containers} as web services that are created, advertised, discovered and invoked
just as elementary web services. The \emph{Container} is
considered as a manager that is responsible for web service
selection upon receiving a request on run-time. The authors have
proposed a scoring service based on non-functional requirements of
the request and web service capabilities to dynamically chose the
web service to perform the requested task. A similar concept was
proposed by Maamar et al. in
\cite{DBLP:journals/ijebr/MaamarSTBB09}. The authors introduced
web service communities as a collection of web services with a
common functionality but different QoS properties. A community
manager, upon receiving a request, delegates the request to one of
its current members. The choice is based on the performance
history and quality metrics of each web service. The authors have
proposed an efficient global web service selection algorithm in
order to approach quality constraints and preferences for
composite services which require aggregation of different types of
services to satisfy the user.

Benslimane et al. \cite{Liris-2770} have proposed a multi-layer
approach grouping similar Web services into communities and having
an interface implemented as an abstract web service for accessing
the community on top of the community layer. The interactions
between composite, management and community layers and the
bindings are performed by a generic driver called Open Software
Connectivity (OSC).

In \cite{managing-hela-jalel}, Limam and Akaichi have proposed web
service communities with centralized access across distributed web
services. They have proposed a framework for web service
management, query resolution among communities and a query caching
mechanism executed by the manager to improve the performance of
query resolution process among many distributed communities. The
key idea is to cache previous computed results for answering
future queries.

Maamar et al. initially in \cite{conf/webist/MaamarLBTS07} and
then comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}
proposed an architecture utilizing \emph{Contract-Net} protocol
for engineering task distribution within communities of web
services. The protocol is centrally executed by the community
manager. This architecture has been further developed in
\cite{CSTintercommunity, conf/IEEEscc/BenharrefSBB11,
conf/IEEEscc/KhosravifarBMMT10, conf/aina/LimTM11}. Two types of
roles have been distinguished for community members: masters and
slaves. Master web services and community managers that lead
communities and are responsible for membership management. They
can invite and convince slave web services to join the community,
and attract new slave web services to their communities by
awarding them better payoff. Moreover, they can eject some slave
members from the community to improve its overall reputation if
these members are misbehaving or cannot provide the promised QoS.

In \cite{Medjahed05adynamic}, Medjahed and Bouguettaya have
developed a community as a ``cluster'' that groups Web services
based on a specific area of interest. All web services in a given
community share the same functionality. These communities are
created by \emph{third party community providers} which use the
\emph{community ontology} as a template and define a set of
operations that all web services within a community should
provide. Using semantic analysis on web service operations, web
services either find and join a community with similar
functionality or create a new operation description for a new
community. The authors have described the concept of
\emph{community agents} associated to \emph{community providers}.
A community agent is responsible, among other things, of the
registration of services with the community. An example of a
community that provides health care services to senior citizens
has been used. In this example, a governmental entity is needed to
check the health care standards used by the members before
authorizing them to be part of the community. Such a central
entity is represented by the community agent. Thus, community
agents are playing the role of community managers. In a close work
\cite{Zeng:2003:QDW:775152.775211}, Zeng et al. have described a
global planning selection algorithm and a delegation algorithm to
be run when a request to execute an operation is received by the
community. This needs a central entity to run those algorithms.
Such entity plays the same role as the community coordinator or
manager.

@@

In this paper, we proposed a training model for the problem of membership management of communities of web services. Using the traning model we created a decision making profile for each community and web service involved which provides them with a set of feasible and utility increasing moves. This utilized our web services with efficient methods of foreseeing how their choices of actions would impact their long-term and short-term goals, therefore they opted for best decision available. The ultimate goal is to choose the best decision when it comes to communities formation, among many possible short-term rational and utility increasing choices. The experimental results show that our algorithms provide web services and community owners, in real-world-like environments, with applicable and near-perfect decision making mechanisms. The results of experiments using real data samples support the need for a long-term training model in a successful decision making process.

Our plan for future work is to advance learning process on the training set that we provided in our work. SVN machine learning algorithm are suitable in classification of our training data set, to better classify correct or wrong decisions based on long-term utility gains, as data set outputs. This can further facilitate the process of finding optimal cooperators in regards to enhancing web services' overall performance as service providers.

\bibliographystyle{elsarticle-num} 
\bibliography{Ehsan}

>>>>

\author{
    \IEEEauthorblockN{\normalsize Ehsan Khosrowshahi Asl\IEEEauthorrefmark{1}, Jamal Bentahar\IEEEauthorrefmark{1}, Hadi Otrok\IEEEauthorrefmark{2}, Babak Khosravifar\IEEEauthorrefmark{1}, Rabeb Mizouni\IEEEauthorrefmark{2}}\\
    \IEEEauthorblockA{\IEEEauthorrefmark{1}Concordia Institute for Information Systems Engineering, Concordia University, Montreal, Canada}
    \\
    \IEEEauthorblockA{\IEEEauthorrefmark{2}Department of Electrical and Computer Engineering, KUSTAR, Abu Dhabi, UAE}
}
\title{Distributed Decision Making for Dynamic Formation of Communities of Web Services}

@@

\begin{abstract}
Web services are loosely-coupled business applications willing to cooperate in distributed settings within different groups called communities. Communities aim to provide web services with better visibility, efficiency, market share and total payoff. A number of mechanisms and models have been recently proposed to aggregate web
services and make them cooperate within their communities. However, existing community models mostly focus on short-term utility gain. Moreover, these models generally suffer from high computational complexity, which makes decision making about community formation in real-time extremely hard, time consuming, and even impossible in some complex cases. In this paper, we propose a strategic distributed decision making mechanism called DDM that regulates web service agents' decision making process, which is about deciding with whom to cooperate. This model first generates a trained set of data based on information obtained from large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc. The decision making mechanism is implemented as a decision tree of viable strategies and their long-term expected utility gain.
%Utilizing the training model, the decision making mechanism implements a decision tree with an estimation of long-term utility gain for the web services. Communities can used the trained model and instantly choose best-response strategies considering their long-term gain. 
Our model helps 1) communities of web services efficiently find the appropriate web service to invite as new member; and 2) single web services find best communities to join. After being trained, web services get to compute expectations as utilities they would gain if they cooperate with communities of different characteristics. In contrast, communities can take the training into account and analyze the characteristics of different individual web services and make prudent decisions when inviting a web service to join or accepting a join inquiry initiated by a web service. In general, DDM equips web services with efficient methods of foreseeing how their choices of actions would impact their short-term and long-term goals, therefore opting for better decisions. We performed experiments using real data from 142 users on 4,532 web services during 64 different time slots. The experimental results show that our algorithms provide web services and community owners, in real-world-like environments, with applicable and near-optimal decision making mechanisms.
\end{abstract}
\begin{IEEEkeywords}
Web services; Community of services; Distributed decision making
\end{IEEEkeywords}

@@

\textbf{Challenges and Problem Statement.} In recent work, communities of web services have been proposed in order to facilitate discovery of web services, improve the Quality of Service (QoS), and help individual services find better market share and opportunities \cite{Zeng:2003:QDW:775152.775211, 10.1109/ARES.2008.7, Paik:2005:TSS:2229263.2230038, Medjahed05adynamic}. However,  two important challenges are to be addressed: 1) choice of the best web services during community development from the community perspective; and 2) choice of the best community to join from the web service perspective. The advocated solutions  \cite{10.1109/ARES.2008.7, conf/webist/MaamarLBTS07, journals/soca/XuYLZB11, 10.1109/TSC.2012.12, managing-hela-jalel, DBLP:conf/IEEEscc/KhosravifarABT11, DBLP:conf/IEEEscc/LimTMB12} have attempted to address these challenges. However, those solutions have two main limits: 
\begin{enumerate}
	\item The solutions consider the architecture of centralized management for communities where most of the decisions are made by the centralized coordinator. The problem is that in real world scenarios, decisions made by independent service providers are highly distributed.
	\item The solutions either propose complex algorithms \cite{10.1109/TSC.2012.12, DBLP:conf/IEEEscc/LimTMB12, journal-community-formation} to find the optimal strategy to follow, or oversimplify the problem by eliminating important parameters and using approximation techniques to make the algorithms tractable \cite{10.1109/TSC.2012.12}.
\end{enumerate}
These approximation methods sometimes negatively influence the outcome because simplifying the constraints may cause important aspects of the problem to be ignored. For instance, instead of calculating the gain distribution using the adequate, but complex shapely-value method, the authors is \cite{10.1109/TSC.2012.12} propose a simple egalitarian way of distributing gain, which completely ignores the gain generated from collaborative work of sub-communities. Other categories of related work, for instance \cite{10.1109/TSC.2012.12, DBLP:conf/IEEEscc/KhosravifarABT11, DBLP:journals/ijebr/MaamarSTBB09}, restrict the decision process within the community coordinator, so other members of the community are not effectively involved. 
%And some other work which do not focus on rationality on web services or communities involved [refrences]. 
In \cite{journal-community-formation}, we proposed a cooperative game-theory-based model for aggregating web services in communities. A centralized decision maker in communities, based on a complete knowledge of available web service quality metrics and performance, has been used to form optimal and stable communities that maximize individual and group income. However, centrality and complete information are strong assumptions, which are not very compatible with real business scenarios.

@@

\subsection{The Join Challenge}\label{s:tjc} 
It has been showed in \cite{10.1109/ARES.2008.7,10.1109/TSC.2012.12,journal-community-formation} that web services can increase their overall utility by collaborating with other web services within communities. This collaboration provides them with better ways of sharing resources and having higher reputation, greater market share and wider visibility. Web services and communities come with different quality metrics, and the long-term outcome depends on these metrics.

@@

\begin{figure}%[!t]
\centerline{\includegraphics[width=5.25in]{figures/steps-final.eps}}
\caption{A summary of DDM decision profile generation steps}
\label{fig_steps}
\end{figure}

@@

In \cite{10.1109/TSC.2012.12}, a cooperative scheme among
autonomous web services based on coalition game theory has been
introduced. The authors have proposed an interesting algorithm to
reach individually stable coalition partition for web services in
order to maximize their efficiency. The communities choose new web
services on the promise that it would benefit the community
without decreasing any other web service's income. In the proposed
model, the worth of community is evaluated with high emphasis on
the availability metric and considering price and cost values
only. The community structure is based on a coordination chain,
where a web service is considered as a \emph{primary} web service
and the community task-distribution method initially invokes the
primary web service and only if the primary web service is
unavailable, the method invokes the next backup web services as
they are ordered in the coordination chain. We believe that this
coordination chain limits the cooperation power as it introduces a
sort of hierarchy. However, in pure and open cooperative models,
such as the one we propose in this paper, active cooperation
activities engaging simultaneously many agents so that they can
perform the tasks more efficiently are being used. Moreover, if
the availability is high, which is the case nowadays with the
recent advancements in cloud infrastructures and hardware technologies, the
backup web services will end-up having a very low chance of
getting jobs, especially the ones further in the chain. This will
results in a considerable waste of web services capabilities.

All the proposed frameworks share a common aspect, which is providing the solution based on assumption of having complete information of all services and performing evaluations based on a large number of input each time they want to adopt a strategic decision making process. 
So basically, these solutions generally suffer from high complexity, which makes decision making very hard, even impossible in some cases in a real-time fashion, or they simplify important aspects to make it practical in the real world, thereby hurting the decision making performance. We address this issue by introducing DDM a framework that operates based on a trained model that regulates web service agents' decision making process in terms of cooperating with one another. After being trained, web services get to compute expectations as utilities they would gain while cooperating with communities of different characteristics. Therefore, web services and communities can make prudent decisions when inviting a web service to join or accepting a join inquiry initiated from a web service. In general, DDM equips web services with efficient methods for foreseeing how their choices will impact their long-term and short-term goals; therefore, opting for best decision available. \\

@@

Here we introduce the related research work regarding the engineering and formation of communities of web services. In \cite{DBLP:journals/internet/BenatallahSD03}, Benatallah et al. defined communities of web services as \emph{Service Containers} that aggregate substitutable web services having the same set of operations and providing common functionalities. They abstracted \emph{Service Containers} as web services that are created, advertised, discovered and invoked just as elementary web services. The \emph{Container} is considered as a manager that is responsible for web service selection upon receiving a request on run-time. The authors have proposed a scoring technique based on non-functional requirements of the request and web service capabilities to dynamically chose the web service to perform the requested task. A similar concept was proposed by Maamar et al. in \cite{DBLP:journals/ijebr/MaamarSTBB09}. The authors introduced web service communities as a collection of web services with a common functionality but different QoS properties. A community manager, upon receiving a request, delegates the request to one of its current members. The choice is based on the performance history and quality metrics of each web service. The authors have proposed an efficient global web service selection algorithm in order to approach quality constraints and preferences for composite services which requires aggregation of different types of services to satisfy the user. In the same line of research, Benslimane et al. \cite{Liris-2770} have proposed a multi-layer approach grouping similar web services into communities and having an interface implemented as an abstract web service for accessing the community. The considered layers are: composite, management and community. The interactions among those layers and the bindings are performed by a generic driver called Open Software Connectivity (OSC). However, unlike our work, these proposals only tackle the problem of internal community management from the task execution perspective, but not the problem of community formation and the one of dynamically selecting which community to join and which web service to invite. Moreover, the web services selection process is done centrally by the community manager, while we address the problem more realistically from the distributed angle.

In \cite{managing-hela-jalel}, Limam and Akaichi have proposed web
service communities with centralized access across distributed web
services. They have proposed a framework for web service
management, query resolution among communities and a query caching
mechanism executed by the manager to improve the performance of
query resolution process among many distributed communities. The
key idea is to cache previous computed results for answering
future queries. Maamar et al. initially in \cite{conf/webist/MaamarLBTS07} and
then comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}
proposed an architecture utilizing \emph{Contract-Net} protocol
for engineering task distribution within communities of web
services. The protocol is centrally executed by the community
manager. This architecture has been further extended in
\cite{CSTintercommunity, conf/IEEEscc/BenharrefSBB11,
conf/IEEEscc/KhosravifarBMMT10, conf/aina/LimTM11}. Two types of
roles have been distinguished for community members: masters and
slaves. Master web services are community managers that lead
communities and are responsible for membership management. They
can invite and convince slave web services to join the community,
and attract new slave web services to their communities by
awarding them better payoff. Moreover, they can eject some slave
members from the community to improve its overall reputation if
these members are misbehaving or cannot provide the promised QoS. 
In \cite{Medjahed05adynamic}, Medjahed and Bouguettaya have
developed a community as a ``cluster'' that groups Web services
based on a specific area of interest. All web services in a given
community share the same functionality. These communities are
created by \emph{third party community providers} which use the
\emph{community ontology} as a template and define a set of
operations that all web services within a community should
provide. Using semantic analysis on web service operations, web
services either find and join a community with similar
functionality or create a new operation description for a new
community. The authors have described the concept of
\emph{community agents} associated to \emph{community providers}.
A community agent is responsible, among other things, of the
registration of services with the community. An example of a
community that provides health care services to senior citizens
has been used. In this example, a governmental entity is needed to
check the health care standards used by the members before
authorizing them to be part of the community. Such a central
entity is represented by the community agent. Thus, community
agents are playing the role of community managers. In a close work
\cite{Zeng:2003:QDW:775152.775211}, Zeng et al. have described a
global planning selection algorithm and a delegation algorithm to
be run when a request to execute an operation is received by the
community. This needs a central entity to run those algorithms.
Such entity plays the same role as the community coordinator or
manager. All these proposals have in common the consideration 
of the central entity for community management, which includes the hiring and firing of the community members, while our approach is fully distributed. Moreover, the stability of the community has not been investigated. Another major difference with our work is that the decision making process is only one way and unilateral from the community manager perspective. In our proposal, both participants, namely communities and web services, participate in the decision making process and a joining decision is made only if it is the best option for both players.

@@

In this paper, we proposed DDM, a strategic distributed decision making mechanism that regulates the community formation process and  membership management in communities of web services. This mechanism helps web services and communities decide with whom to be grouped and cooperate. DDM first generates a trained set of data based on information obtained from large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc. Communities and web services can use the trained model and instantly choose best-response strategies considering their long-term gain. In fact, the decision making mechanism is implemented as a decision tree of possible viable strategies along with their long-term expected utility. The ultimate goal of our mechanism is to choose the best decision when it comes to community formation, which goes beyond short-term utility increasing choices, usually considered in the literature. The experimental results show that our approach allows web services and communities, in real-world-like environments, to make near-perfect decisions. The results of experiments using real data samples support the need for a long-term training model in a successful decision making process.

Our plan for future work is to advance further the learning process on the training set we provided in our work by leveraging some game theoretical approaches. In fact, game theory provides powerful techniques for strategic decision making, particularly cooperative and coalition formation games. Hedonic games and fractional hedonic games are of particular interest where the utility of a player in a community depends on the identity of the other members of the community and the value this player ascribes to those members. We intent to investigate stability solution concepts such as Shapely value so that long-term decisions will be based on the probability that the community will stay for long period.

%The SVM machine learning algorithm is suitable for classification of our training data set to better distinguish  decisions based on long-term utility, as data set outputs. This can further facilitate the process of finding optimal cooperators in regards to enhancing web services' overall performance as service providers.

\bibliographystyle{elsarticle-num} 
\bibliography{Ehsan1}
